Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-03-30 paper_latex_edit - Copy.tex
txs auto checkin

Where \begin{math}\gamma \end{math}, \begin{math}\ N_{s} \end{math}, \begin{math}\ N_{i} \end{math} and \begin{math}\ N_{t} \end{math} are compression ratio, codeword length, selected rows from \begin{math}\tilde{H} \end{math} and number of transmit antenna.where \(N_s\) is the real-valued codeword length, and \(2 N_i N_t\) accounts for the real/imaginary parts of \(\tilde{\mathbf{H}}_f\).

>>>>

Where \begin{math}\gamma \end{math}, \begin{math}\ N_{s} \end{math}, \begin{math}\ N_{i} \end{math} and \begin{math}\ N_{t} \end{math} are compression ratio, codeword length, selected rows from \begin{math}\tilde{H} \end{math} and number of transmit antenna.\(N_s\) is the real-valued codeword length, and \(2 N_i N_t\) accounts for the real/imaginary parts of \(\tilde{\mathbf{H}}_f\).
